\documentclass[10pt,a4paper]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MODIFY:
\newcommand{\projectname}{Comparing a Neural Network and Knowledge-Based Approach for Crowd Dynamics} % - PROJECT NAME
\newcommand{\duedate}{2024-02-08} % - DEADLINE DATE
\newcommand{\authorA}{Alejandro Hernandez Artiles (03785345)}
\newcommand{\authorB}{Pavel Sindelar (03785154)}
\newcommand{\authorC}{Haoxiang Yang (03767758)}
\newcommand{\authorD}{Jianfeng Yue (03765255)}
\newcommand{\authorE}{Leonhard Chen (03711258)}
\newcommand{\groupNumber}{C} % - YOUR GROUP NUMBER
\newcommand{\exerciseNumber}{6} % - THE NUMBER OF THE EXERCISE

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% IMPORTS:
\input{imports.tex}
\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{float}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\frontpage

\begin{task}{1, Introduction of Approach and Dataset (15\%)}
\begin{itemize}
    \item Introduce a neural network and knowledge-based approach.
    \item Define the datasets from paper \cite{tordeux2020prediction} (\url{https://zenodo.org/records/1054017}).
\end{itemize}
    
\end{task}

\begin{task}{2, Implementation of the neural network (40\%)}
\begin{itemize}
    \item Implement neural network from paper (and potentially more complex model).
    \item Tests on corridor and bottleneck experiment.
\end{itemize}

\end{task}

\begin{task}{3, Implementation of knowledge-based model (20\%)}
\begin{itemize}
    \item Implementation of a knowledge-based model (Weidmann Fundamental Diagram).
    \item Tests on corridor and bottleneck experiment.
\end{itemize}
\end{task}

\begin{task}{4, Comparison of the approaches (20\%)}
\begin{itemize}
    \item Compare the test results.
    \item Discussion of the approaches and architectures (benefits, drawbacks, challenges).
\end{itemize}

\end{task}

\begin{task}{5, Discussion of future work and other approaches (5\%)}
\begin{itemize}
    \item Introduce approach separate from paper \cite{korbmacher2022review}.
    \item Discuss hybrid approaches.
\end{itemize}

\end{task}
%%%%%%%%%%%%%%%%%%%%%%%%%%%  REFERENCES
\bibliographystyle{plain}
\bibliography{Literature}
\end{document}